%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{orange}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=.9]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Stefano}{Yushinski}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
%\address{2342 S. Rosewood St.}{Philadelphia, PA 19145}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\phone[mobile]{+1~(267)~266~9424}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+1~(215)~334~3}                      % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{syushinski@gmail.com}                        % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{Aug. 2017-- May 2021}{B.S.E in Computer and Information Science}
{University of Pennsylvania}{Philadelphia}{\textit{GPA: 3.13, Major: 3.27}}{}  % arguments 3 to 6 can be left empty

\cvitem{Relevant Courses}{Intro to Computer Systems, Automata Computability \& Complexity,
 Data Structures and Algorithms, Operating Systems, Intro to Cryptography and Networks,
 Software Design \& Engineering, Data Analytics in R, Intro to Algorithms, Computer Organization and Design,
 Product Design, Hardware and Software Co-Design for Machine Learning Performance, Database \& Info Systems}

\section{Experience}
\subsection{Vocational}
\cventry{July 2021-- Present}{Software Engineer 1}{Payroll \& Workermanagement Capabilities}{Intuit}{Mountain View, CA}{
  Worked with a team to develop a user experience that would allow customers to migrate from legacy software to Quickbooks.
  Additionally, worked on solving customer problems to benefit their experience in viewing their company reports. 
  And, consolidated front end plugins into one maintainable plugin that is easier to manage.
}
\cventry{Spring 2021}{Teaching Assistant}{HW \& SW Co-Design for ML}{University of Pennsylvania}{}
{
  Provided office hours for students to help them grasp conceptual ideas on a broad array of machine learning concepts
  and how to improve performance of machine learning models by leveraging parallel processes, and downsizing models to make them
  more accessible on edge devices.
}
\cventry{Summer 2020}{Software Engineer Intern}{Quickbooks Integration \& Automation}{Intuit}{Mountain View, CA}{
  Worked on improving Quickbooks automation by integrating machine learning models into the frontend codebase,
  as well as improving UX and quickfixing bugs.
}
\cventry{May 2019-- July 2019}{Engineering Research Intern}{National University
 of Singapore}{Singapore}{}{Researched machine learning models and their 
 accuracy for localizing sensor nodes in an indoor wireless sensor network for
  a mobile life sign monitor medical device. More about the research project,
  \textbf{Localization of Sensor Nodes}, is mentioned below.}
\cventry{June 2018-- Sept. 2018}{Front End App Developer Intern}{Teamtrics}
{Philadelphia}{}{Learned and executed conceptual front end frameworks of an
 Android app and single handedly developed the Front End in the native language 
 of Java via Android Studio. }

\subsection{Projects}
\cventry{}{FPGA-Accelerated Matrix Mult. for CNN}{HW \& SW Co-Design for ML}{University of Pennsylvania}{}
{
Used Vivado High Level Synthesis and HDL techniques to develop a FPGA accelerated Matrix Mult. 
to run on the VGG-16 CNN. Programmed the hardware accelerated layers using Vivado HLS as well as C, and
C\texttt{++}. Also, built a C\texttt{++} extension to replace the conv2d layers of VGG-16 with the aforementioned FPGA accelerated layers
in Python, and then benchmarked results in Python.
}
\cventry{}{PennOS}{Operating Systems}{University of Pennsylvania}{}
{Worked with a team to develop an operating system with a proper scheduler, file system and shell.
Worked on the file systems, as well as integrating the file systems with the scheduler and shell.
Developed skills in cooperation with a team on an extensive project built in C as well as 
understandable code for the API of the file systems.}
\cventry{}{Kinitro}{Software Design \& Engineering}{University of Pennsylvania}{}{
    Worked with a group to full-stack develop a mobile app for Android using Android Studio for 
    frontend and Node.js as our backend. Later on translated the front end to build it on 
    React Native for interest of learning. }
\cventry{}{Localization of Sensor Nodes}{Mobile Life Signs Monitor}{National University of Singapore}{}{
  Collected data and curated it to train multiple models to test the 
  performance of Neural Networks, SVMs, and Multiple Linear Regression
  using sklearn-expertsys and TensorFlow in Python to localize sensor nodes
  within an indoor low energy bluetooth sensor network. 
}
%----------COMPUTER SKILLS---------------
%\section{Computer skills}

%\cvitem{}{\textsc{C}, \textsc{OCaml}, \textsc{javascript}, \LaTeX,
%\textsc{TensorFlow}, \textsc{scikit-learn}, \textsc{react-redux},
%\textsc{react native}, \textsc{java}, \textsc{python}, \textsc{assembly}, 
%\textsc{android studio}, \textsc{R}, \textsc{SQL}}


%-----       letter       ---------------------------------------------------------
% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle

%\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.

